\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-09-17 paper.tex
Revise up to the SEM images. Remove them.

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=1.2\textwidth]{j_Ivsxy.png}
  \includegraphics[width=\textwidth]{j_Ivsx.png}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
    the surface of the sample through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.03\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
    along the center line $y=0.74\,\text{cm}$ (bottom
    panel).}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with aspect ratios closer to 1.

\subsection{PS GRIN Films }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
  \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x_1=0.2\text{cm}$,  $x_2=0.4\text{cm}$, $x_3=0.6\text{cm}$,
    $x_4=0.8\text{cm}$, $x_5=1\text{cm}$, $x_6=1.2\text{cm}$,
    $x_7=1.4\text{cm}$, $x_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. During the preparation the cathode was over
    the leftmost point $x_1$.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig. \ref{fig:SI3} applying a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. Thus, we may expect our formula \eqref{Eq:J}
to fail close to the border, at distances of the order of the radius
of the cross-section of the o-ring.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions $(x,y)$
    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
    $x=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR}} and \eqref{Eq:Brugg}.
  \label{fig:R20}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \,\text{mA}$
    during a time $t_1=600\,\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\,\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\,\text{cm}$ and
  $x_C=1.7\,\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_3$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I_3=20\,\text{mA}$
 for a time $t=250\,\text{s}$. We employed the same geometry as that described in
 Sec. \ref{sec:current-density}
The positions $\bm R_n=(x_n,y_n)$, $n=1\ldots8$  with
$x_n=0.2n\,\text{cm}$ and $y_n=0.74\,\text{cm}$ on which reflectance
spectra were measured are indicated. The electrode was situated above
the position $\bm R_1$  corresponds to the left side of the
photograph. The variation of the optical properties across the
sample is evident. \notaL{Tenemos algo sensato que decir sobre el
  gradiente en la dirección vertical cerca de los bordes?}

The thicknesses of the layer were measured
using SEM. In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
$G_1$ taken at the
positions $A$, $B$, and $C$ shown in
Fig. \ref{fig:DR3}. From these micrographs we can
obtain the thicknesses of the porous layer at different
positions. Thus, we obtained that for our sample $G_1$
$d_{1A}= 1320\,\text{nm}$, $ d_{1B} = 997\,\text{nm}$, and $d_{1c} = 605
\,\text{nm}$.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/semD11}
  \caption{Side-view SEM micrographs of the PS GRIN single layer
    taken at positions $A$, $B$, and $C$ of sample $G_1$ shown in
    Fig. \ref{fig:DR3}.
    \notaL{Quité la info redundante}}
  \label{fig:DR4}
\end{figure}
We fitted then reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosities $p_{1A}$, $p_{1B}$ and $p_{1C}$ as
adjustable parameters and using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg}. We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
measured one, though its interference oscillations are larger towards
the blue region probably due to the lack of surface scattering in our
calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
the complex index of refraction corresponding to the fitted porosities.
Similarly, for a second sample $G_2$, etched with a
larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$.

>>>>

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=1.2\textwidth]{j_Ivsxy.png}
  \includegraphics[width=\textwidth]{j_Ivsx.png}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
    the surface of the sample through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
    along the center line $y=0.74\,\text{cm}$ (bottom
    panel).}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with different aspect ratios.

\subsection{PS GRIN Films }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
  \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$G_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to fail close to the border, at distances of the order of the radius
of the cross-section of the o-ring, of the order of a milimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n$ as the distance to the sealing o-ring,
which differed by $0.14\,\text{cm}$ from the corresponding distance
$x_n$ to the wall of the cell.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR}} and \eqref{Eq:Brugg}.
  \label{fig:R20}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \,\text{mA}$
    during a time $t_1=600\,\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\,\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\,\text{cm}$ and
  $x_C=1.7\,\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}

\ifexclude
The thicknesses of the layer were measured
using SEM. In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
$G_1$ taken at the
positions $A$, $B$, and $C$ shown in
Fig. \ref{fig:DR3}. From these micrographs we can
obtain the thicknesses of the porous layer at different
positions. Thus, we obtained that for our sample $G_1$
$d_{1A}= 1320\,\text{nm}$, $ d_{1B} = 997\,\text{nm}$, and $d_{1c} = 605
\,\text{nm}$.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/semD11}
  \caption{Side-view SEM micrographs of the PS GRIN single layer
    taken at positions $A$, $B$, and $C$ of sample $G_1$ shown in
    Fig. \ref{fig:DR3}.
    \notaL{Quité la info redundante}}
  \label{fig:DR4}
\end{figure}
\fi %exclude
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. ****AQUIVOY***

 We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
measured one, though its interference oscillations are larger towards
the blue region probably due to the lack of surface scattering in our
calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
the complex index of refraction corresponding to the fitted porosities.
Similarly, for a second sample $G_2$, etched with a
larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$.
